% Abstract checklist:
%  http://users.ece.cmu.edu/~koopman/essays/abstract.html
%
% Subject
% Motivation
% Problem statement
% Approach
% Results
% Conclusions

This thesis describes a cryptographically secured decentralized peer-to-peer file sharing system, bundled as a JavaScript developer library called \emph{Rymd}. This includes evaluating current web technologies and determining if they are sufficient to implement such a system.

The problem domain includes how to make the system secure, decentralized, anonymous and modular using web technologies. The motivation behind developing such a system lies in giving control of typically centralized services, such as messaging or storage and sharing of files, back to users. By making the system highly modular, we manage to achieve satisfying results in reliability and technical agnosticism with regards to underlying implementations.

Default implementation modules of the core functionality in Rymd are given. Alongside Rymd a web application, \emph{Shuttle}, that injects these modules into Rymd is developed. IndexedDB is used for persistent data and key storage while peer-to-peer communication is achieved through WebRTC. Common cryptographic services such as encryption, decryption, signing and more are done through the Web Cryptography API. The Namecoin blockchain is used for storing user identities mapped to their public encryption keys, which in turn are used to verify peer identities.

Even though this project succeeds with its goal of creating a client-side file sharing platform, the technologies used are in such a premature state that they cannot fully satisfy security goals. We are confident that the standard bodies and browser vendors will continue their work on bringing open web technologies up to speed with their native counterparts.
