\lettrine[lines=2, findent=2pt]{I}{n a day} and age where people all over the world own more than one digital device~\cite{OFCOMa:Online}~\cite{OFCOMb:Online}, there is a growing need for services which let users easily store, access, synchronize, and share personal files. The internet makes it possible to store data \emph{in the cloud} and access it from a web browser or a designated client. Instead of storing files on physical media, it is today a common practice to use services such as Dropbox, Google Drive, or Apple's iCloud for home and business matters. In November 2013, Dropbox reached 200 million users~\cite{Constine:2013:Online}. Google Drive is integrated across a large number of Google's products. Similarly, Apple's iCloud stores and synchronizes personal preferences across devices and applications for iOS and OS X users~\cite{CloudTrend:Online}.

The existing mainstream services mentioned above are centralized, which means that the files and resources stored with them are placed on central servers somewhere on the internet. This report describes the results of developing a file sharing system that runs independently on each participant's computer and does not rely on any central server - a decentralized system. The system will build on the preconception that direct connections are only made between peers that have pre-existing knowledge of each other. Such networks could still allow friend-to-friend propagation of data and searches in several steps to connect users to vast networks of resources through chains of friends of friends. Focus will be on security and open web standards.


\input{sections/background.tex}
\input{sections/purpose.tex}
\input{sections/problem.tex}
\input{sections/scope.tex}
\input{sections/structure.tex}
