There is a plethora of technologies for distributing and synchronizing data between peers that at a first glance may look very similar to Rymd. Below are some more well-known and similar pieces of software. The features described will hopefully highlight how they relate to each other and Rymd.

\begin{description}
  \item[Bittorrent Sync]~\cite{BitTorent:2014:Online} is a distributed peer-to-peer multi-way file syncing software using the Bittorrent protocol for file transfers. Synchronized folders are mapped directly to the underlying file system, and each folder is encrypted using a shared secret key. Public-key cryptography is not employed, and the only available clients are closed-source binary applications using the network of the creator, Bittorrent Inc. While they do have a developer API, it requires developer keys issued from Bittorrent Inc.
  \item[RetroShare]~\cite{Retroshare:2014:Online} markets itself as a Friend-2-Friend decentralized communication platform which uses GPG to create a Web of Trust between peers. The Friend-2-Friend search works by propagating search and file transfers recursively to all friends of friends to a certain degree of separation. In this way, users can search for files from a huge network while still only staying directly connected to people that they trust. It is, however, a very large project: The application provides file-sharing, instant messaging, discussion forums, e-mail, Voice over IP (VoIP) and group chat. It is open source and distributed as cross-platform binaries.
  \item[ShareFest]~\cite{Sharefest:2014:Online} is a peer-to-peer one-to-many file-sharing web based software using WebRTC data channels. ShareFest can be seen as a more limited and primitive version of what Rymd aims to be: ShareFest can share files over WebRTC channels, but does not accommodate authentication, persistence or local encryption. It does, however, operate on a mesh network similar to Bittorrent. Other similar WebRTC-based P2P file sharing web applications but without additional cryptographic properties include RTCCopy and ShareDrop.
  \item[Freenet]~\cite{Freenet:2014:Online} is one of the first \emph{darknets}, consisting of a distributed, decentralized data store that uploads files with strong anonymity across a network. Each node in the network also acts as a cache for the content stored in the network. Files are generally split up in parts that are distributed, and when fetching files it is unfeasible to determine the origin and sender of the files. Focusing on anonymity, free speech and plausible deniability, the encryption is done in the communication and storage layers. Because of this design, Freenet is quite slow. Files can be retrieved using the cryptographic key used to upload them. Freenet is free software built with Java.
  \item[Tahoe-LAFS]~\cite{Tahoe:2014:Online}, or Tahoe Least-Authority Filesystem, is a distributed, encrypted and redundant file system. It distributes encrypted files across a predetermined set of servers and allows sharing of both mutable and immutable files. There is a web-interface, but similar to all other user-interfaces it has to go through a \emph{gateway} where encryption and server-communication is performed. Users will typically run their own gateways and will thus need to accommodate hosting for them.
  \item[Bitmessage]~\cite{Bitmessage:2014:Online} is a P2P distributed messaging system intended to replace e-mail. Public keys of all participants are distributed over the entire network, and can be retrieved using their fingerprints (which are used as addresses). In order to send a message, it is encrypted using the receiver's public key and sent to the entire network. Participants try to decrypt every message, and will so be able to retrieve the ones they can decrypt. Messages are stored in the network for two days. There is thus no way to tie messages to senders and recipients.

\end{description}

Rymd differentiates by being the only project so far that combines the properties of open source, purely web based, decentralized and cryptographically secured. Additionally, it is a developer-geared library rather than a user-oriented application.
